### 2014-04-17 pot/LaTeX/skewnormal.tex
Working on the algebra for the posterior distributions

We first specify a model for the complete data, $Y_t(\bs)$, and then study the induced model for thresholded data, $\Yt_t(\bs)$.  
The full data model is given in Section \ref{s:model} assuming a multivariate normal distribution with a different variance each day.
Computationally, the values below the threshold are updated using standard Bayesian missing data methods as described in Section \ref{s:comp}.

\subsection{Complete data}\label{s:model}
Consider the spatial process
\begin{align} \label{eq:fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + e_t(\bs)\\
  e_t(\bs) &= \sigma \delta | u_t(\bs) | + v_t(\bs)
\end{align}
where $u_t(\bs) = u_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $u_{tl} \iid N(0, 1)$, $\delta \in (-1, 1)$ controls skew, and $v_t(\bs)$ is a spatial process with mean zero and variance $\sigma^2(1 - \delta^2)$.
Then $Y_t(\bs)$ is skew normal within each partition \citep{Minozzo2012}.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that $P_{tl}$ includes all spatial locations $\bs$ that are within the partition.
Then
\begin{align} \label{eq:hier}
    Y_t(\bs) \mid \Theta &= \mu_t(\bs) + v_t(\bs) \\
    \mu_t(\bs) &= X_t(\bs) \beta + \sigma \delta | u_{tl} |
\end{align}
where $l = \argmin_j ||\bs - w_j ||$ and $\Theta = \{ u_{t1}, \ldots, u_{tL}, w_{t1}, \ldots, w_{tL}, \beta, \rho, \nu, \sigma \}$ are the random effects, knot locations, and parameters for the mean, and spatial covariance.

@@

\section*{Appendix A.1: Posterior distributions}
\input{halfnormal.tex}
\input{betapost.tex}

@@

\bibliographystyle{rss}
\bibliography{Schlather}

>>>>

We first specify a model for the complete data, $Y_t(\bs)$, and then study the induced model for thresholded data, $\Yt_t(\bs)$.  
The full data model is given in Section \ref{s:model} assuming a skew normal distribution with a different variance each day.
Computationally, the values below the threshold are updated using standard Bayesian missing data methods as described in Section \ref{s:comp}.
The skew normal representation is from \citep{Minozzo2012} and is the sum of a normal and half-normal random variable.
\subsection{Half-normal}\label{s:hn}
Let $u = \xi + \sqrt{\eta} |z|$ where $Z \sim N(0, 1)$.
Then $U$ follows a half-normal distribution, $U \sim \mbox{HN}(\xi, \eta )$ \citep{Wiper2008}, and the density is given by 
\begin{align}
  f_U(u) = \frac{ \sqrt{\pi} }{ \sqrt{2 \eta} } \exp \left( - \frac{ (u-\xi)^2 }{ 2 \eta } \right), \quad u > \xi.
\end{align}

\subsection{Complete data}\label{s:model}
Consider the spatial process
\begin{align} \label{eq:fullmodel}
  Y_t(\bs) &= X_t(\bs) \beta + e_t(\bs)\\
  e_t(\bs) &= u_t(\bs) + v_t(\bs)
\end{align}
where $u_t(\bs) = \sigma \delta |z_t|$, $z_t(\bs) = z_{tl}$ if $s \in P_{tl}$ where $P_{t1}, \ldots, P_{tL}$ form a partition, and $z_{tl} \iid N(0, 1)$, $\delta \in (-1, 1)$ controls skew, and $v_t(\bs)$ is a spatial process with mean zero and variance $\sigma^2(1 - \delta^2)$.
Then $Y_t(\bs)$ is skew normal within each partition \citep{Minozzo2012}.
We model this with a Bayesian hierarchical model as follows.
Let $w_{t1}, \ldots, w_{tL}$ be partition centers so that $P_{tl}$ includes all spatial locations $\bs$ that are within the partition.
Then
\begin{align} \label{eq:hier}
    Y_t(\bs) \mid \Theta &= X_t(\bs) \beta + u_t(\bs) + v_t(\bs) \\
    u_t(\bs) \mid \Theta &\sim \mbox{Half-Normal}(0, \sigma \delta)\\
    v_t(\bs) \mid \Theta & \sim \Matern(0, \Sigma)\\
    \sigma &\sim \mbox{IG}(\alpha, \beta)\\
    \delta &\sim \mbox{U}(-1, 1)
\end{align}
where $l = \argmin_j ||\bs - w_j ||$, $\Theta = \{u_{t1}, \ldots, u_{tL}, w_{t1}, \ldots, w_{tL}, \beta, \sigma, \delta, \rho, \nu \}$ and $\Sigma$ is a \Matern covariance matrix with variance $\sigma^2 (1 - \delta^2)$

@@

\section*{Appendix A.1: Posterior distributions}
\input{upost.tex}
\input{betapost.tex}
\input{sigpost.tex}

@@

\bibliographystyle{rss}
\bibliography{skewnormal}
